---
title: "HW 3"
format: html
editor: visual
---

## Lubridate Assignment

### Problem 1:

• Load the wmata_ridership data frame into R from https://dcgerard.github.io/stat\_ 412_612/data/wmata_ridership.csv. For each month, calculate the proportion of rides made on a given day of the month. Then make box plots of the proportions of ridership vs day of the weak. But exclude any days from 2004 and 2005.

```{r}
library(tidyverse)
library(dplyr)
library(lubridate)
wmata <- read.csv("wmata_ridership.csv")
```

```{r}
wmata$Date <- ymd(wmata$Date)
wmata_filtered <- wmata %>%
  filter(year(Date) != 2004 & year(Date) != 2005)

wmata_filtered <- wmata_filtered %>%
  mutate(month = month(Date),
         day_of_week = wday(Date, label = TRUE)) %>%
           group_by(month, day_of_week) %>% summarise(total_rides = sum(Total)) %>%
    ungroup()

wmata_filtered <- wmata_filtered %>%
  group_by(month) %>%
  mutate(proportion = total_rides / sum(total_rides))

ggplot(wmata_filtered, aes(x = day_of_week, y = proportion)) +
  geom_boxplot() +
  facet_wrap(~month, scales = "free_x") +
  labs(x = "Day of the Week", y = "Proportion of Rides") +
  theme_minimal()

```

### Problem 2:

• Write only one line of the code to return only the leap years fo years 2024, 3021, 2000 or 1800, 800, 5050, 600 and 7156.

```{r}
years <- c(2024, 3021, 2000, 1800, 800, 5050, 600, 7156)

years[years %% 4 == 0 & (years %% 100 != 0 | years %% 400 == 0)]

```
